A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks

### 2013-09-20 PAPER/implementation.tex
Fixes
added pics
Final fix to typos

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{pictures/disr_imp.eps}
  \caption{\emph{DiSR} block architecture.}
 \label{fig:implementation}
\end{figure}

@@

As discussed above, one of the main design challenge of DNA
Self-Assembled systems is the limited resource available for
implementing both computations and routing decisions for each node.
For this reason, assuming a budget of $10^4$ CNFETs for each network's
node~\cite{liu_jetcs} we estimated the required resource for
implementing the entire DiSR block. An not optimized VHDL description
of the DiSR circuitry has been written and synthesized at gate-level.
Considering the specific layout of each single logic elements ( NAND,
full-adder, latch etc.), it has been possible to get a rough estimate
of the number of transistors necessary for implementing the DiSR
logic.  Figure~\ref{fig:imp_trend} shows the results of synthesis in
terms of number of devices (CNFETs) versus the number of network nodes
while the network scales up from $10\times10$ to $100\times100$ nodes.
\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{pictures/imp_rslt.eps}
  \caption{DiSR synthesis results: N is the number of network's node.}
 \label{fig:imp_trend}
\end{figure}
In particular, observing the Fig.\ref{fig:imp_trend} can 
be pointed out that the proposed implementation occupy  about 20\% of the node budget. 
Further, more than the absolute number of devices itself, it is interesting to
observe that, while the node have a squared increment, the circuitry
complexity which implements the DiSR algorithm increases with a slowly
growing trend.  
An intuitive explaination of this is the relatively simple logic of
DiSR, whose behaviour is almost code on scalable storage structures.
For example, the number of registers implementing the
\emph{link\_visited[]} and \emph{link\_tvisited[]} table follow the
logaritmic function:
\begin{equation}
  \label{eq:imp_trend}
  N_{reg}=2\cdot N_{port} \cdot log_2(N)
\end{equation}
where $N_{port}$ is the number of the router's ports, $N$ is the number 
of network's nodes while the term $2$ takes in account that \emph{link\_visited[]} and 
\emph{link\_tvisited[]} are two separate set of registers. While this number is fixed by 
the number of network's node, the control circuitry could be optimized applying more effort 
in future designs of this building block.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.25\textwidth]{pictures/disr_imp.eps}
  \caption{\emph{DiSR} block architecture.}
 \label{fig:implementation}
\end{figure}

@@

As discussed above, one of the main design challenge of DNA
Self-Assembled systems is the limited resource available for
implementing both computations and routing decisions for each node.
For this reason, assuming a budget of $10^4$ CNFETs for each network's
node~\cite{liu_jetcs} we estimated the required resource for
implementing the entire DiSR block. A not optimized behavioural
HDL of the DiSR circuitry has been written and synthesized at gate-level.
Considering the specific layout of each single logic elements ( NAND,
full-adder, latch etc.), it has been possible to get a rough estimate
of the number of transistors necessary for implementing the DiSR
logic.  Figure~\ref{fig:imp_trend} shows the results of synthesis in
terms of number of devices (CNFETs) versus the number of network nodes
while the network scales up from $10\times10$ to $100\times100$ nodes.
\begin{figure}
  \centering
  \includegraphics[width=0.25\textwidth]{pictures/imp_rslt.eps}
  \caption{DiSR synthesis results: N is the number of network's node.}
 \label{fig:imp_trend}
\end{figure}
In particular, observing the Fig.\ref{fig:imp_trend} can 
be pointed out that the proposed implementation occupy  about 20\% of the node budget. 
Further, more than the absolute number of devices itself, it is interesting to
observe that, while the node have a squared increment, the circuitry
complexity which implements the DiSR algorithm increases with a slowly
growing trend.  
An intuitive explanation of this is the relatively simple logic of
DiSR, whose behaviour is almost code on scalable storage structures.
For example, the number of registers implementing the
\emph{link\_visited[]} and \emph{link\_tvisited[]} table follow the
logarithmic function:
\begin{equation}
  \label{eq:imp_trend}
  N_{reg}=2\cdot N_{port} \cdot log_2(N)
\end{equation}
where $N_{port}$ is the number of the router's ports, $N$ is the number 
of network's nodes while the term $2$ takes in account that \emph{link\_visited[]} and 
\emph{link\_tvisited[]} are two separate set of registers. While this number is fixed by 
the number of network's node, the control circuitry could be optimized applying more effort 
in future designs of this building block.

### 2013-09-20 PAPER/introduction.tex
Final fix to typos

In the last years, Self-assembled nanoscale architectures~\cite{winfree1998, yan2003}
are emerging as a promising technology due their tera/peta scale of
integration, defect tolerance tolerance and huge potential computing
capabilities. These technologies are certainly still at
their early stage of development, however different laboratory demos and
prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006_1, pistol2009}.
%, patwardhan2006
The main idea behind this approach is to exploit the physical regularity and
stabiliy of DNA structures in order to create a scaffold onto which
nano-devices (e.g. nanowires and CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be
attached. This can be achieved by designing approapriate complementary DNA tags for
each terminal to be placed, so that a nano device will be attached
only where its own DNA tag matches a complementary tag on the DNA grid
scaffold.
%(see figure~\ref{fig:dna_tag}.
%
%\begin{figure}
%  \centering
%    \includegraphics[width=0.30\textwidth]{pictures/dna2b.eps}
%  \caption{DNA tag matching}
%  \label{fig:dna_tag}
%\end{figure}
A detailed description of the chemical properties involved is far
beyond the scope of this paper (see also~\cite{braun1998, seeman1999}), so we will focus on
the three main challenges that this new fabrication process introduces
in Computer Design: \emph{(i) limited node complexity}, \emph{(ii) large scale
randomness} and \emph{(iii) high defect rates}.

@@

Finally, \emph{defect rates}: while they are very hardly tolerated in mask
based top down design , the same nature of a bottom up self
assembled process cannot assume such a deterministic device placement
process, thus defect tolerance is something like a design requirement
more than a exception to be avoided.

These aspects of a DNA-self assembly process lead to some important
implications to be addressed when approaching to the design of
computer architecture: a computational model should be founded on a
distributed network of small computing and storage nodes, randomly
placed and interconnected (see figure~\ref{fig:nana}).
Proof-of-concept of such kind of computational model can be found for
example in~\cite{patwardhan2006_1}.  Since no regularity can be
assumed in such network, a topology agnostic strategy that avoids
deadlock should be adopted in order to route packets (e.g.
instructions and data operands) among nodes.  It is important to
underline that, altought we can assume an architecture similar to the
one depicted in~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not stricly dependent on any of the
underlying computing architecture.

@@

The paper is organized as follows: in Section~\ref{sec:related_works}
we summarize the main approaches to topology agnostic routing. Next in
Section~\ref{sec:disr_concepts} are described the main elements of the
proposed approach, showing a the DiSR execution model in
Section~\ref{sec:execution_model}.  In Section~\ref{sec:simulation}
simulations are carried out with the opensource tool Nanoxim to
demostrate how DiSR preserves some of the main segment-based
properties and how compares to the tree-based approaches. Finally a
draft of a architectural implementation is shown in
Section~\ref{sec:implementation} to evaluate the feasibility of the
approach in terms of node complexity.

\section{Related Works}
\label{sec:related_works}
Several works~\cite{sancho2002, skeie2002, skeie2004, koibuchi2003} have been presented addressing the problem of topology
agnostic routing. While they show interesting
performances, the requirement for virtual channels resources 
to avoid deadlock makes them not suitable for the specific DNA self
assembled networks we are assuming as background.
Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} do not use virtual channels to
achieve deadlock freedom, but turn proibitions. 
In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
topology, then placing bidirectional restrictions by avoiding a packet
to traverse the same link in both up and down directions.
While the hierarchical nature of this approach can lead to uneven traffic
distribution, with many packets traversing upper links (near to the
root), this is quite acceptable in classical wide area networks
topologies with a limited number of nodes. Other approaches such as
FX~\cite{sancho2000} mitigate this
issue, but the set of turn restrictions is still prefixed,
striclty depending on the particular tree root selected. 
Other solutions try to approach the issue of irregular
topologies by limiting the number~\cite{dally1994, duato1997, gomez2004, koibuchi2008} or the
location~\cite{zhang2008, sui2000, flich2008, liu2011} of missing links. This
restriction is clearly unacceptable given the hight-defect rates of
DNA self-assembled networks scenario. For the same reason, we also
avoid considering solutions based on hardware-redundancy to
dynamically recover defects as in~\cite{constantinides2006, kohler2010, kim2006, park2006}.

In~\cite{mejia_ipdps06} authors present SR, an approach the solves these
limitations by allowing turn restrictions to be placed locally,
independently from other restrictions. The whole network is
partitioned into segments, and a each bidirectional turn
restriction can be freely chosen within a segment in order to guarantee
deadlock freedom and connected networks. This \emph{locality
independence} property, together with no requirement of any particular tree/root
choice, would make it the best choice for the given scenario;
however, its topology independency still requires the knowledge of the
whole network graph in order to find the segments.

The DiSR approach presented in this work is a first attempt of
reaching the same goals of a segment based approach, that is
estabilishing segments, without requiring any topology graph or
centralized execution.

>>>>

In the last years, Self-assembled nanoscale architectures~\cite{winfree1998, yan2003}
are emerging as a promising technology due their tera/peta scale of
integration, defect tolerance tolerance and huge potential computing
capabilities. These technologies are certainly still at
their early stage of development, however different laboratory demos and
prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006_1, pistol2009}.
%, patwardhan2006
The main idea behind this approach is to exploit the physical regularity and
stability of DNA structures in order to create a scaffold onto which
nano-devices (e.g. nanowires and CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be
attached. This can be achieved by designing appropriate complementary DNA tags for
each terminal to be placed, so that a nano device will be attached
only where its own DNA tag matches a complementary tag on the DNA grid
scaffold.
%(see figure~\ref{fig:dna_tag}.
%
%\begin{figure}
%  \centering
%    \includegraphics[width=0.30\textwidth]{pictures/dna2b.eps}
%  \caption{DNA tag matching}
%  \label{fig:dna_tag}
%\end{figure}
A detailed description of the chemical properties involved is far
beyond the scope of this paper (see also~\cite{braun1998, seeman1999}), so we will focus on
the three main challenges that this new fabrication process introduces
in Computer Design: \emph{(i) limited node complexity}, \emph{(ii) large scale
randomness} and \emph{(iii) high defect rates}.

@@

Finally, \emph{defect rates}: while they are very hardly tolerated in mask
based top down design , the same nature of a bottom up self
assembled process cannot assume such a deterministic device placement
process, thus defect tolerance is something like a design requirement
more than an exception to be avoided.

These aspects of a DNA-self assembly process lead to some important
implications to be addressed when approaching to the design of
computer architecture: a computational model should be founded on a
distributed network of small computing and storage nodes, randomly
placed and interconnected (see figure~\ref{fig:nana}).
Proof-of-concept of such kind of computational model can be found for
example in~\cite{patwardhan2006_1}.  Since no regularity can be
assumed in such network, a topology agnostic strategy that avoids
deadlock should be adopted in order to route packets (e.g.
instructions and data operands) among nodes.  It is important to
underline that, altougth we can assume an architecture similar to the
one depicted in~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not strictly dependent on any of the
underlying computing architecture.

@@

The paper is organized as follows: in Section~\ref{sec:related_works}
we summarize the main approaches to topology agnostic routing. Next in
Section~\ref{sec:disr_concepts} are described the main elements and
the execution model of the proposed approach.  In Section~\ref{sec:simulation}
simulations are carried out with the opensource tool Nanoxim to
demonstrate how DiSR preserves some of the main segment-based
properties and how compares to the tree-based approaches. Finally a
draft of a architectural implementation is shown in
Section~\ref{sec:implementation} to evaluate the feasibility of the
approach in terms of node complexity.

\section{Related Works}
\label{sec:related_works}
Several works~\cite{sancho2002, skeie2002, skeie2004, koibuchi2003} have been presented addressing the problem of topology
agnostic routing. While they show interesting
performances, the requirement for virtual channels resources 
to avoid deadlock makes them not suitable for the specific DNA self
assembled networks we are assuming as background.
Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} do not use virtual channels to
achieve deadlock freedom, but turn prohibitions. 
In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
topology, then placing bidirectional restrictions by avoiding a packet
to traverse the same link in both up and down directions.
While the hierarchical nature of this approach can lead to uneven traffic
distribution, with many packets traversing upper links (near to the
root), this is quite acceptable in classical wide area networks
topologies with a limited number of nodes. Other approaches such as
FX~\cite{sancho2000} mitigate this
issue, but the set of turn restrictions is still prefixed,
strictly depending on the particular tree root selected. 
Other solutions try to approach the issue of irregular
topologies by limiting the number~\cite{dally1994, duato1997, gomez2004, koibuchi2008} or the
location~\cite{zhang2008, sui2000, flich2008, liu2011} of missing links. This
restriction is clearly unacceptable given the hight-defect rates of
DNA self-assembled networks scenario. For the same reason, we also
avoid considering solutions based on hardware-redundancy to
dynamically recover defects as in~\cite{constantinides2006, kohler2010, kim2006, park2006}.

In~\cite{mejia_ipdps06} authors present SR, an approach the solves these
limitations by allowing turn restrictions to be placed locally,
independently from other restrictions. The whole network is
partitioned into segments, and each bidirectional turn
restriction can be freely chosen within a segment in order to guarantee
deadlock freedom and connected networks. This \emph{locality
independence} property, together with no requirement of any particular tree/root
choice, would make it the best choice for the given scenario;
however, its topology independency still requires the knowledge of the
whole network graph in order to find the segments.

The DiSR approach presented in this work is a first attempt of
reaching the same goals of a segment based approach, that is
establishing segments, without requiring any topology graph or
centralized execution.

### 2013-09-20 PAPER/paper.tex
Final fix to typos

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}

@@

\begin{abstract}
In this paper we present DiSR, a first effort for a distributed
segment-based approach to routing and defect mapping in a nano-scale,
topology agnostic scenario based on DNA self-assembly. The main aim is
exploiting the already-proven qualities of segment-based routing
without neither requiring a topology graph as input, nor needing a
centralized algorithm to configure network paths.  After introducing
the conceptual elements and the execution model of DiSR, we show how
the opensource Nanoxim platform has been used to evaluate the proposed
approach in the process of discovering irregular network topology
while estabilishing network segments.  Results show how DiSR still
preserves some important properties (coverage, defect tolerance,
scalability)  while avoiding centralized tree-based broadcasting and
resource hungry solutions such as virtual channels and hardware
redundancy. Finally, we analyzed a first, not yet optimised gate-level
hardware implementation of the required control logic and storage for
DiSR, demonstrating a relatively acceptable impact ranging from 10 to
about 20\% of the budget of transistors available for each node.
\end{abstract}

@@

\section{Conclusions}
In this work we presented DiSR, a initial attempt of porting a segment based
approach to distributed self-assembled nanoscale scenario. We
demostrated how DiSR can accomplish the aim of finding a segment
coverage of the network withouth requiring any centralized approach
that would request a graph topology as input. A draft hardware
implementation has been presented to evalute the impact on the limited
node size typical of the assumed scenario. Future works will focus on
developing self tuning of DiSR to match a high coverage levels and the
detailed low level hardware implementation on
DNA grid using the appropriate nano devices models.

>>>>

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}
\renewcommand{\baselinestretch}{0.98}\normalsize
%------------------------------------------------------------------------------

@@

\begin{abstract}
In this paper we present DiSR, a first effort for a distributed
segment-based approach to routing and defect mapping in a nano-scale,
topology agnostic scenario based on DNA self-assembly. The main aim is
exploiting the already-proven qualities of segment-based routing
without neither requiring a topology graph as input, nor needing a
centralized algorithm to configure network paths.  After introducing
the conceptual elements and the execution model of DiSR, we show how
the opensource Nanoxim platform has been used to evaluate the proposed
approach in the process of discovering irregular network topology
while establishing network segments.  Results show how DiSR still
preserves some important properties (coverage, defect tolerance,
scalability)  while avoiding centralized tree-based broadcasting and
resource hungry solutions such as virtual channels and hardware
redundancy. Finally, we analyzed a first, not yet optimised gate-level
hardware implementation of the required control logic and storage for
DiSR, demonstrating a relatively acceptable impact ranging from 10 to
about 20\% of the budget of transistors available for each node.
\end{abstract}

@@

\section{Conclusions}
In this work we presented DiSR, an initial attempt of porting a segment based
approach to distributed self-assembled nanoscale scenario. We
demonstrated how DiSR can accomplish the aim of finding a segment
coverage of the network without requiring any centralized approach
that would request a graph topology as input. A draft hardware
implementation has been presented to evaluate the impact on the limited
node size typical of the assumed scenario. Future works will focus on
developing self tuning of DiSR to match a high coverage levels and the
detailed low level hardware implementation on
DNA grid using the appropriate nano devices models.

### 2013-09-20 PAPER/simulation.tex
Final fix to typos

%------------------------------------------------------------------------------
\subsection{Experimental setup}
The following parameters have been taken into account when
performing the DiSR simulation:
\begin{itemize}
\item {\emph{Size of the network}}: number of nodes, on a
range from 10x10 to 100x100 sized networks. 
%\item {\% defective links}: the probability that each link is
%disconnected or not present, from 0 the amount that yelds
%no more segments.
\item {\emph{\% defective nodes}}: the probability that a node is not
working, thus having all its links cannot be utilized during DiSR setup.  
%Same range as defective links parameter.
\item {Bootstrap node}: the node used from upper layer 
to inject the DiSR process. When not explicitly investigating the
impact of each single bootstrap choice, a set representative regions have been
considered, i.e. the central part of the network and the edge corners
\end{itemize}

The show the results, the following evaluation metrics have been adopted:
\begin{itemize}
\item{Node coverage}: this is the fraction of nodes that
are assigned to a segment. In the ideal case, all the non defective
nodes should be assigned, so this metric is useful to show how some
disconnected node regions can negativaly impact on the whole DiSR
effectiveness.
\item{Broadcast latency}: this measures how the time required to complete the
segment assignment scale for increasing network sizes and defect rates
\item{Bootstrap node effect}: this evaluates the impact of the chosen
bootstrap node on the node coverage.
\end{itemize}

Further, to evaluate how DiSR compares against the centralized segment
based algorithm, the following metrics have been adopted:
\begin{itemize}
%\item {Average Path Lenght}:
%\item {Average Link Weight}:
\item {Unidirectional restrictions:}
\item {Number of Segments}:
\end{itemize}

@@

\section{Results}
\label{sec:results}

In Figure~\ref{fig:coverage} is shown node coverage using different
network sizes and bootstrap injection points. As can be seen,
increasing the \% of defective node, TODO COMMENT...

\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.22\textwidth]{pictures/set1.eps} & 
    \includegraphics[width=0.22\textwidth]{pictures/coverage.eps} \\
    \includegraphics[width=0.22\textwidth]{pictures/set2.eps} & 
    \includegraphics[width=0.22\textwidth]{pictures/set3.eps} \\
    (a) & (b)
  \end{tabular}
  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
  \label{fig:bootstrap}
\end{figure}

Figure~\ref{fig:bootstrap} shows the effect of bootstrap node position
on node coverage, for different defect rates. TODO COMMENT.

Next, Figure~\ref{fig:latency_size} shows latency as function of
network size, with different defect rates, while Figure~\ref{fig:latency_defective}
shows the same latency when different bootstrap nodes are
considered.... TODO COMMENT

TODO: something like Broadcast Tree properties (sez.  5.4)

>>>>

%------------------------------------------------------------------------------
\subsection{Experimental setup}
The following parameters have been taken into account when
performing the DiSR simulation:
\begin{itemize}
\item {\emph{Size of the network}}: number of nodes, on a
range from 10x10 to 100x100 sized networks. 
%\item {\% defective links}: the probability that each link is
%disconnected or not present, from 0 the amount that yelds
%no more segments.
\item {\emph{\% defective nodes}}: the probability that a node is not
working, thus having all its links cannot be utilized during DiSR setup.  
%Same range as defective links parameter.
\item {\emph{Bootstrap node}}: the node used from upper layer 
to inject the DiSR process. When not explicitly investigating the
impact of each single bootstrap choice, a set representative regions have been
considered, i.e. the central part of the network and the edge corners
\end{itemize}

The show the results, the following evaluation metrics have been adopted:
\begin{itemize}
\item{Node coverage}: this is the fraction of nodes that
are assigned to a segment. In the ideal case, all the non defective
nodes should be assigned, so this metric is useful to show how some
disconnected node regions can negatively impact on the whole DiSR
effectiveness.
\item{\emph{Latency}}: this measures how the cycles required to complete the
segment assignment scales for increasing network sizes and defect rates
\item{\emph{Bootstrap node effect}}: this evaluates the impact of the chosen
bootstrap node on the node coverage.
\end{itemize}

%Further, to evaluate how DiSR compares against the centralized segment
%based algorithm, the following metrics have been adopted:
%\begin{itemize}
%%\item {Average Path Lenght}:
%%\item {Average Link Weight}:
%\item {Unidirectional restrictions:}
%\item {Number of Segments}:
%\end{itemize}

@@

\subsection{Results}
\label{sec:results}

Figure~\ref{fig:results} collects the results in terms of node
coverage and latency at different network sizes, defect rates and
bootstrap injection points.  In particular graphs (a) and (b) show
node coverage for DiSR and RPF tree based approach respectively. While
the first aim of DiSR is not to reach the optimal coverage, we still
can observe a quite good performance as compared to tree based
approach. Note that defect rates beyond 25\% lead to many disconnected
regions of nodes that this first of DiSR cannot handle; however, these
level of defects should be considered as worst case scenarios, so the
achieved coverage of $0.5$ is satisfying results for this first
version of DiSR. As regards the the network size it seems to have a
limited impact when defect rate do not introduce to much disconnected
regions.

The number of cycles required to complete the segment mapping
process is shown in latency graph (c). Comparison against tree-based
has been omitted for space reasons, however similar numbers (in terms
of upper bound) have been reported
(see~\cite{Patwardhan05evaluatingthe} for details). What it's more
interesting is to observe is how DiSR latency scales with network
size. For example, going from 900 to 2500 nodes, at the medium defect
rate of $0.15$, leads to an increase from 3000 to 4500 cycles. Note how
the effect of defect rate is increasing until the threshold of $0.25$
is reached, meaning that while DiSR finds it more difficult to
complete the process due increasing defective paths, it still discover
new segments when let running for a more extended amount of cycles.
After that threshold, the impact of entire disconnected regions
becomes predominant and DiSR more quickly complete the process
covering the nodes that can be reached.

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.22\textwidth]{pictures/set1.eps} & 
\includegraphics[width=0.22\textwidth]{pictures/coverage.eps} \\
(a) & (b) \\
\includegraphics[width=0.22\textwidth]{pictures/set2.eps} & 
\includegraphics[width=0.22\textwidth]{pictures/set3.eps} \\
(c) & (d)
\end{tabular}
\caption{DiSR (a) and RPF (b) node coverage (c) Latency and effect
of bootstrap node (d)}
\label{fig:results}
\end{figure}

Finally, picture (d) visually represent  the stability of the approach
against different choices of the bootstrap node in a 10x10 network.
This is an important aspect to evaluate when considering that one of
the main advantages of DiSR against all the tree based approaches
should be the ability of choosing whatever bootstrap node, without
having to care of any particular \emph{root-node role} assumed in the future.
In other words, after segments have been established, the bootstrap node
is like every other node, i.e. it is not center of a structure, and it
is not an hotspot for the traffic distribution. The results in terms
of coverage,  shown for low, medium and high defect profiles, seems to
demonstrate a relatively limited impact of the bootstrap choice in
the low/medium scenarios, while a 30\%instability is found for very high defect
rates. This also sounds acceptable, since when lot of defective nodes
are present, the particular position of the bootstrap choice could
lead to completely different evolution in the DiSR setup process.
